---
title: "Ways towards A Net-Zero Society, Take NYC as an Example"
author: "Xinye Wang, Yiyang Cheng, Zhenhao An, Hanlu Xu"
subtitle: "19-603 Project Sprint #01:"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
opts_chunk$set(echo = FALSE,
               out.width = "75%", 
               fig.align = "center")
```
## Updated Research Question

## Updated Data Sources
Our GitHub Repo for data and code: <https://github.com/Ritsuko-xu/19433-2000wattCommunity/>
You can browse our dataset files and data source citations under "dataset" subfolder.

- 01. The economic, demographic and social dataset will be from Census Bureau <https://data.census.gov/advanced>. This is one of the best data source for such analysis related to society and population.
- 02. NYC open data, where we can find building benchmarking data The NYC Benchmarking Law requires owners of large buildings to annually measure their energy and water consumption in a process called benchmarking. <https://data.cityofnewyork.us/Health/rodent-bbl/2brg-uyvv/data>
- 03. NYC open data. BBL dataset mapping buildings to longtitude and latitude coordinates. <https://www.nyc.gov/site/planning/data-maps/open-data/dwn-edesignations.page>
- 04. A dataset mapping census tracts to zip code areas. This dataset is used for spation join operations. <https://www.huduser.gov/portal/datasets/usps_crosswalk.html#data>

## 3. Research Progress
- 01. Joined census data in #01 dataset into buildings energy consumption data in #02 dataset
- 02. Created model for electricity consumption ~ household income

```{r}
# set correct working directory
setwd("D:/OneDrive/education/S23_CMU/19-603_Data_Science_for_Technology_Innovation_and_Policy/19433-2000wattCommunity")
library("tidyverse")
```

```{r}
# load benchmarking table
BR <- read.csv(file = paste0(getwd(),"/dataset/NYC_Building_Energy_with_GEOID/table.csv"),
                 header=TRUE)

BR


```

